Sailing the High Seas:\\ A Christian Exploration of Piracy

### 2024-04-10 paper.tex
finish conclusion

\section{Conclusion}

@@

\begin{enumerate}
  \item In response to economic argument: Would the pirate have bought the
    product/service in the first place?
\end{enumerate}

\begin{displayquote}
  Of additional concern is the fact that by making \textins{Intellectual Property}
  theft a national security threat without being clear about what actually
  constitutes intellectual property, not only does the U.S. government create a
  new reason for a militarized Internet, but it also sets the stage for companies
  to assert that a range of other activities from file sharing to producing
  counterfeit DVDs threaten national security and require further state
  intervention.~\cite[p. 264]{halbert:agendas}
\end{displayquote}

\subsection{Applications}

\subsection{Further Work}

>>>>

\section{Conclusion}
In closing, piracy and its related tools are not as cut and dry of an issue as one might
initially be led to believe. On one hand, piracy facilitates the spread of illegal goods
and services. Pirated software from an untrusted source may also contain malware and the
act of piracy itself, from one perspective, takes business and money away from companies.
On the other hand, piracy can be a powerful force for good. It assists in the
dissemination of information that is dangerous to oppressive regimes and it ensures that
people of all financial backgrounds can access and contribute to valuable research for the
benefit of everyone. More generally, the goal of piracy is to keep information free and
open to everyone; in that regard, it promotes equality of access to human thoughts.

@@

By far, one of the most common arguments raised against piracy, as highlighted previously,
is that piracy steals money from businesses because it demotivates people from paying for
their products and services. While this may be true in many cases, the reality is a little
more nuanced. Someone who chooses to pirate a product rather than purchase it may not have
bought the product in the first place if piracy was not an option. On top of that, if
someone really enjoys using the pirated version of a piece of software, they might choose
to pay for the legitimate version of it to support the developers and get new updates
faster. Even if the user refuses to pay for software, distributing the pirated version of
software helps popularize it. When something gets really popular, people want to try it
and that leads to more people who might decide to support the company who develops it by
purchasing the real version.

Regardless of the potential benefit of piracy, businesses still see it as a clear threat
to their bottom line and try their best to protect their intellectual property at the
expense of the consumer's open access to information. \blockcquote[264]{halbert:agendas}
{Of additional concern is the fact that by making \textins{Intellectual Property} theft a
national security threat without being clear about what actually constitutes intellectual
property, not only does the U.S. government create a new reason for a militarized
Internet, but it also sets the stage for companies to assert that a range of other
activities from file sharing to producing counterfeit DVDs threaten national security and
require further state intervention.}

With how advanced piracy technology has become and how it will continue to improve, it
will not be going away anytime soon. With that in mind, Christians should make an effort
to seek the ways in which the tools of piracy enable the spread of the Gospel and how it
can be used as a salt and a light to those in less fortunate places---fellow Christians
and unbelievers alike.
